---
title: "4 First Contact with R"
output: html_document
---

# 4.3 Exercises
**1)** Here’s the list of monthly expenses for a hypothetical undergraduate student
- cell phone $80
- transportation $20
- groceries $550
- gym $15
- rent $1700
- other $85
a. Using the `console` pane of RStudio, create objects (i.e. variables) for each of these expenses listed above, and then create an object `total` with the sum of the expenses.

```{r}
cell_phone <- 80
transportation <- 20
groceries <- 550
gym <- 15
rent <- 1700
other <- 85

# Total assignment operator
monthly_total <- cell_phone + transportation + groceries + gym + rent + other
monthly_total
```

b. Assuming that the student has the same expenses every month, how much would she spend during a school “semester”? (assume the semester involves five months). Write code in R to find this value.

```{r}
semester_total <- 5 * monthly_total
semester
```


c. Using the same assumption about the monthly expenses, how much would she spend during a school “year”? (assume the academic year is 10 months). Write code in R to find this value.

```{r}
year_total <- 10 * monthly_total
year_total
```

2) Write code in the console to calculate: 3x^2 + 4x + 8 when x = 2

```{r}
x = 2
3*x^2 + 4*x + 8
```

3) Calculate: 3x^2 + 4x + 8 but now with a numeric sequence for using x <- -3:3

```{r}
x <- -3:3
3*x^2 + 4*x + 8
```
